Learning to communicate using recursive pragmatic reasoning about other agents

### 2013-05-31 praglearn.tex
fix wonky phrasing

One option is to continue iterating such
strategies until reaching a fixed point equilibrium. While this
strategy guarantees that each agent will behave normatively given the
other agent's strategy, there is no guarantee that such strategies
will be near the system's global optimum. More importantly, is there much
evidence that humans do not use such equilibrium strategies; their behavior in language
games (and in other games \cite{camerer2004}) can be well-modeled as
implementing $S_n$ or $L_n$ for some small $n$
\cite{frank2012}. Following this work, we recurse a finite (small)
number of times. The consequence is that one agent, implementing
$S_n$, is fully optimal with respect to the game, while the other,
implementing $L_{n-1}$, is only nearly optimal---off by a single
recursion.

>>>>

One option is to continue iterating such
strategies until reaching a fixed point equilibrium. While this
strategy guarantees that each agent will behave normatively given the
other agent's strategy, there is no guarantee that such strategies
will be near the system's global optimum. More importantly, there is a
great deal of
evidence that humans do not use such equilibrium strategies; their behavior in language
games (and in other games \cite{camerer2004}) can be well-modeled as
implementing $S_n$ or $L_n$ for some small $n$
\cite{frank2012}. Following this work, we recurse a finite (small)
number of times. The consequence is that one agent, implementing
$S_n$, is fully optimal with respect to the game, while the other,
implementing $L_{n-1}$, is only nearly optimal---off by a single
recursion.
